Deeply Virtual Compton Scattering measurement off bound proton

### 2018-07-12 eg6-letters/incoherent/incoherent_prl.tex
edit the acknowledgment for ahmed's institution

The authors acknowledge the staff of the Accelerator and Physics Divisions at 
the Thomas Jefferson National Accelerator Facility who made this experiment 
possible. This work was supported in part by the Chilean Comisi\'on Nacional de 
Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), the Italian Instituto 
Nazionale di Fisica Nucleare, the French Centre National de la Recherche 
Scientifique, the French Commissariat \`a l'Energie Atomique, the U.S.  
Department of Energy under Contract No. DE-AC02-06CH11357, the United Kingdom 
Science and Technology Facilities Council (STFC), the Scottish Universities 
Physics Alliance (SUPA), the National Research Foundation of Korea, and the 
Office of Research and Economic Development at Mississippi State University.  
M.~Hattawy also acknowledges the support of the Consulat G\'en\'eral de France 
\`a J\'erusalem.  The Southeastern Universities Research Association operates 
the Thomas Jefferson National Accelerator Facility for the United States 
Department of Energy under Contract No. DE-AC05-06OR23177.

>>>>

The authors acknowledge the staff of the Accelerator and Physics Divisions at 
the Thomas Jefferson National Accelerator Facility who made this experiment 
possible. This work was supported in part by the Chilean Comisi\'on Nacional de 
Investigaci\'on Cient\'ifica y Tecnol\'ogica (CONICYT), by CONICYT PIA grant 
ACT1413, the Italian Instituto Nazionale di Fisica Nucleare, the French Centre 
National de la Recherche Scientifique, the French Commissariat \`a l'Energie 
Atomique, the U.S.  Department of Energy under Contract No. DE-AC02-06CH11357, 
the United Kingdom Science and Technology Facilities Council (STFC), the 
Scottish Universities Physics Alliance (SUPA), the National Research Foundation 
of Korea, and the Office of Research and Economic Development at Mississippi 
State University.  M.~Hattawy also acknowledges the support of the Consulat 
G\'en\'eral de France \`a J\'erusalem.  The Southeastern Universities Research 
Association operates the Thomas Jefferson National Accelerator Facility for the 
United States Department of Energy under Contract No. DE-AC05-06OR23177.
